Proposed Solution

### 2017-01-25 CAV17/secs/eval.tex
cav17: eval and learner

\section{Evaluation}

We evaluate this approach using our implementation, \app.
For our training set, \trainingSet, we use a preexisting set of 256 industrial MySQL configuration files collected in previous configuration analysis work~\cite{xu15systems}.
For our test set we collected 1000 MySQL configuration from Github, and filtered the poorly formatted files out for a final total of 973 files.
In our evaluation we focus on MySQL for consistency, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.

@@

However, we are able to manually determine that some errors are true positives by search forums like StackOverflow for records that particular configuration settings have cause problems on real-world systems.

>>>>

\section{Implementation and Evaluation}

We have implemented a \app prototype, and evaluated it based on
real-world configuration datasets.

\subsection{Prototype Implementation}

\ennan{put the implementation as one or more paragraphs.}

\subsection{Evaluation}

To evaluate our \app prototype, we need to have two datasets:
1)a training set and 2) a dataset for testing. 
For our training set, \trainingSet, we use a preexisting set of 256 
industrial MySQL configuration files collected in previous configuration 
analysis work~\cite{configdataset}.
The majority of configuration files in this training set are incorrect.
For our evaluation, we collected 1000 MySQL configuration files 
from Github, and filtered the poorly formatted files out for a final 
total of 973 files, called as {\em test set}.
In our evaluation we focus on MySQL for consistency, 
but \app can handle any configuration language (that can be parsed to 
the intermediate representation from Sec.~\ref{sec:trans}).
We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.

@@

However, we are able to manually determine that some errors are true
positives by searching forums like StackOverflow for records that
particular configuration settings have cause problems on real-world
systems.

### 2017-01-25 CAV17/secs/learner.tex
cav17: eval and learner

The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
We use slightly modified definitions of of these to handle arbitrary predicates as rules.
During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
%
\begin{equation*}
 support(r) = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
\end{equation*}
\begin{equation*}
 confidence(r) = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
\end{equation*}

@@

\begin{align}
Learn(\trainingSet) = \{r | \ &support(r) > t_s\ \land \nonumber \\
    & confidence(r) > t_c\ \land \label{eq:learn}\\ 
    & X,\ Y \subset \keys\} \nonumber
\end{align}

\subsection{Error Classes}
Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $X, Y$.
Ordering errors have $|X|, |Y| = 1$ and use the predicate $order$ to mean the keyword $X$ must come before the keyword $Y$ in any configuration file.
Missing keyword entry errors also require $|X|, |Y| = 1$ and use the predicate $missing$ to mean the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
The type rule is a set of rules over multiple predicates, which take the form $X \implies isType\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).

@@

With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
\app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
Then, the checker applies the learner from Eq.~\ref{eq:learn}, $Learn(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
The checker will then report the following set of errors:

\begin{align*}
Errors(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
                               & r \in Learn(\trainingSet) \ \land \\
                               & r \notin Learn(\mathcal{V})
\end{align*}

>>>>

The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
We use slightly modified definitions of of these to handle arbitrary predicates as rules.
During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
%
\begin{equation*}
 \textit{support(r)} = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
\end{equation*}
\begin{equation*}
 \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
\end{equation*}

@@

\begin{align}
Learn(\trainingSet) = \{r | \ &support(r) > t_s\ \land \nonumber \\
    & \textit{confidence(r)} > t_c\ \land \label{eq:learn}\\ 
    & X,\ Y \subset \keys\} \nonumber
\end{align}

\subsection{Error Classes}
Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $X, Y$.
Ordering errors have $|X|, |Y| = 1$ and use the predicate $order$ to mean the keyword $X$ must come before the keyword $Y$ in any configuration file.
Missing keyword entry errors also require $|X|, |Y| = 1$ and use the predicate $missing$ to mean the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
The type rule is a set of rules over multiple predicates, which take the
form $X \implies \textit{isType}\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).

@@

With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
\app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
Then, the checker applies the learner from Eq.~\ref{eq:learn},
$\textit{Learn}(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
The checker will then report the following set of errors:

\begin{align*}
\textit{Errors}(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
                               & r \in \textit{Learn}(\trainingSet) \ \land \\
                               & r \notin \textit{Learn}(\mathcal{V})
\end{align*}
